### 2022-05-24 paper.Rmd
table and figure caption

apa_table(
  tab,
  caption = "Results of the simulation study",
  note = "The global results of the simulation study aggregated across all conditions. Cells contain information about the average between-group discrepancy with regard to means, standard deviations, skewness, kurtosis, and correlations. Lower values indicate less discrepancy, i.e., higher between-group similarity. Each cell value is the result of averaging across 30,000 data points (10,000 data sets $\\times$ $K = 2$, $K = 3$, $K = or 4$).",
  escape = FALSE,
  align = c("r")
)

@@

```{r Figure1, fig.width = 8, fig.height = 10}

>>>>

apa_table(
  tab,
  caption = "Results of the simulation study",
  note = "The global results of the simulation study aggregated across all conditions. Cells contain information about the average between-group discrepancy with regard to means, standard deviations, skewness, kurtosis, and correlations. Lower values indicate less discrepancy, i.e., higher between-group similarity. Each cell value is the result of averaging across 30,000 data points (10,000 data sets $\\times$ $K = 2$, $K = 3$ or $K = 4$).",
  escape = FALSE,
  align = c("r")
)

@@

```{r Figure1, fig.width = 8, fig.height = 10, fig.cap = "Simulation results by $N$."}
